Predicting Covid Data

### 2022-12-05 main.rmd
update edits

## The Monte Carlo Study

- In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error to predict future trends of covid data spread.
- Add more stuff here...

## Ciufolini and Paolozzi's Study

@@

## The Gauss Error function

- The Gauss Error function is widely accepted as a good way to model the spread of covid data, especially in China. By using
the Gauss Error function, we can predict the spread of covid data in the future for other countries.
- $a+b*erf(c*x-d)$

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases), color = "red") +
  labs(x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1, color="blue") +
  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]))
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2, color="blue") +
  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]))
```

@@

## Works Cited
- Link to study:
- I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
- Link to covid data:
- https://covid19.who.int/

>>>>

## The Monte Carlo Study:

**Mathematical prediction of the time evolution of the COVID-19 pandemic in Italy by a Gauss error function and Monte Carlo simulations**

<br>

*Author: Ignazio Ciufolini, Antonio Paolozzi*

## Introduction : Ciufolini and Paolozzi's Study

* In this study by Ignazio Ciufolini and Antonio Paolozzi, they use a Gauss Error function that approximates the distribution of the cumulative positive cases of COVID-19 in China
  * They have then use the function to approximate the number of cumulative positive cases in Italy
  * Then performed a 150 Monte Carlo simulations to predict the peak and valley of the number of daily positive cases and fatalities
* This study do not take into account factors such as daily nasopharyngeal swabs, medical, social distancing, etc.

## Cont.

@@

## Overview of the Monte Carlo Simulation

* create a random matrix : m X n
  * m = number of random outcomes (*chosen to be 150*)
  * n = number of observed days (*n = 1,...,j*)
* each # in the matrix is a Gaussian distribution with mean = 1 and sigma = 0.1
  * multiply each column (*j*) by the # of total cases (or deaths) that corresponds to each day *j* **#FIXME#**
- add more...

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
gauss_fn <- function(x,a,b,c,d) {a+b*erf(c*x-d)}
model1 <- nls(total_cases ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
# summary(model1)$parameters
fn_model1 <- function(x) {4.017e+04 + 4.047e+04 * erf(9.284e-02 * x - 1.732e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_cases), color = "red") +
  labs(x = "Days", y = "China cumulative number of cases") +
  stat_function(fun=fn_model1) +
  geom_segment(aes(x = peak1, y = 0, xend = peak1, yend = china$total_cases[ceiling(peak1)]), color="blue")
```

@@

```{r, results=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
model2 <- nls(total_deaths ~ gauss_fn(days,a,b,c,d), data=china, start=list(a=10000,b=10000,c=0.1,d=1))
#summary(model2)$parameters
fn_model2 <- function(x) {1.571e+03 + 1.658e+03 * erf(6.194e-02 * x - 1.533e+00)}
ggplot(data = china) +
  geom_point(aes(x = days, y = total_deaths), color = "red") +
  labs(x = "Days", y = "China cumulative number of fatalities") +
  ylim(0,5000) +
  stat_function(fun=fn_model2) +
  geom_segment(aes(x = peak2, y = 0, xend = peak2, yend = china$total_deaths[ceiling(peak2)]), color="blue")
```

@@

# Monte Carlo Simulations

## China

## Italy

## Australia

## Works Cited
- Link to study:
- I. Ciufolini, A. Paolozzi, Prediction of the time evolution of the Covid-19 Pandemic in Italy by a Gauss
Error Function and Monte Carlo simulations. Submitted to BioRxiv on 03.26.2020 and transferred on
03.27.2020 to MedRxiv. https://doi.org/10.1101/2020.03.27.20045104
- Link to covid data:
- https://covid19.who.int/
- source to find the second derivative of fitted function:
- https://proofwiki.org/wiki/Derivative_of_Error_Function
